Enhancement of SDR in Thessaloniki

### 2024-04-14 high_aod/GHI_enh_06_sza.tex
Commit 2024-04-14 06:14

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-03-14}

@@

{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{4}
\tableofcontents
}
\newpage
\FloatBarrier

@@

\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza-1} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza-2} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza-3} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-1} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-2} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-3} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-4} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-5} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-6} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-7} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-8} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-9} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-10} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-11} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-12} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-13} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-14} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-15} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-16} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-17} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-18} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-19} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-20} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-21} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-22} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-23} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-24} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-25} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-26} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-27} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-28} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-29} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-30} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-31} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-32} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-33} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-34} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-35} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_month-36} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_doy-1} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_doy-2} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_doy-3} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{/home/athan/MANUSCRIPTS/02_enhancement/GHI_enh_06_sza_files/figure-latex/sza_doy-4} \end{center}

@@

\begin{verbatim}
2024-03-14 19:41:18.5 athan@tyler GHI_enh_06_sza.R 0.846766 mins
\end{verbatim}

>>>>

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-04-13}

@@

{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{4}
\tableofcontents
}
\begin{verbatim}

Attaching package: 'zoo'
\end{verbatim}

\begin{verbatim}
The following objects are masked from 'package:data.table':

    yearmon, yearqtr
\end{verbatim}

\begin{verbatim}
The following objects are masked from 'package:base':

    as.Date, as.Date.numeric
\end{verbatim}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-1} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-2} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza-3} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-1} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-2} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-3} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-4} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-5} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-6} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-7} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-8} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-9} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-10} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-11} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-12} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-13} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-14} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-15} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-16} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-17} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-18} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-19} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-20} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-21} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-22} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-23} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-24} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-25} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-26} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-27} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-28} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-29} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-30} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-31} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-32} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-33} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-34} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-35} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_month-36} \end{center}

@@

\begin{verbatim}
Warning: A numeric `legend.position` argument in `theme()` was deprecated in ggplot2 3.5.0.
i Please use the `legend.position.inside` argument of `theme()` instead.
This warning is displayed once every 8 hours.
Call `lifecycle::last_lifecycle_warnings()` to see where this warning was generated.
\end{verbatim}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_doy-1} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_doy-2} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_doy-3} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_06_sza_files/figure-latex/sza_doy-4} \end{center}

@@

\begin{verbatim}
2024-04-13 18:20:39.7 athan@tyler GHI_enh_06_sza.R 0.320738 mins
\end{verbatim}
